%MC samples are used to study the effect of different showering generators on the kinematics and decay properties of 
%heavy flavor hadrons produced in \ttbar\ and di-jet events. 

The versions of the four generators studied here are 
\PythiaS\ 6.427, 
\PythiaEE\ 8.175, 
\Herwig\ 6.520 
with \Jimmy\ 4.31~\cite{Butterworth:1996zw} for the underlying event and
\Herwigpp\ 2.6.3a.
All \pp\ samples have been generated with a center-of-mass energy of $\sqrt{s}=8$~\TeV.  

Two physics
processes are studied:
\begin{itemize}

  \item Top-pair production (\ttbar ) is calculated using  
\PowHeg\ ~\cite{Nason:2004rx, Frixione:2007vw, Alioli:2010xd, Alioli:2008gx} r2330 and
the \textsc{CT10}~\cite{Lai:2010vv} parton distribution functions (PDFs).  At keast one of the $W$ bosons in the \ttbar\ event is required to decay leptonically.
The output of \PowHeg\ are files in Les Houches Event (LHE) format, which contain the top-pair decay products (leptons and
quarks). The same 
\PowHeg\ LHE files are then passed to each of the four generators 
for parton shower, hadronization and underlying-event modeling.
The generator tunes used are
Perugia 2011C~\cite{Skands:2010ak} (\Pythia ),
AU2(CT10)~\cite{ATL-PHYS-PUB-2012-003} (\PythiaE )~\footnote{
While the default release of Pythia 8.175 uses the tau lifetimes specified in the \PowHeg\ LHE files, a patch was applied to overrule the incorrect lifetimes written out in the \PowHeg\ event record. This patch has since become part of \PythiaEE~8.175.},
%While the default release of \PythiaEE~8.175 did not
%properly set the $\tau$ lifetime, a patch to fix this problem was applied to the samples studied here.
AUET2(CT10)~\cite{ATL-PHYS-PUB-2011-008} (\Jimmy)
and UE-EE-4-LO**~\cite{Seymour:2013qka} (\Herwigpp ).  
In \Pythia\ and \PythiaE, heavy quark fragmentation uses the Lund symmetric model with
the Bowler modification~\cite{Bowler:1981sb}.  In \Herwig\ and \Herwigpp, heavy quarks are fragmented using the cluster model. 

\item High \pT~jet samples are generated using the matrix
element calculations provided by each generator.  The generator tunes and fragmentation models used are
the same as those used for the \ttbar\ samples. Events are required
to have at least one jet with \pT\ between 500~\GeV\ and 1~\TeV.

\end{itemize}


For both processes, jets are reconstructed from stable particles~\footnote{Stable particles are defined as those with a mean lifetime, $c\tau_{0}$,~$< 10$~mm.} using the
infrared- and collinear-safe \antikt\ algorithm~\cite{bib:antikt2}
with radius parameter $R=0.4$ using the FastJet package~\cite{bib:antikt3}. In the case of \ttbar\ samples, leptons
from the W decay are excluded from the jet recontruction.


For the fragmentation studies in Section~\ref{sec:fragmentation},~$e^+e^-$ samples are generated.
%\Pythia, \PythiaE, \Herwigpp and \Herwig. 
Unless otherwise stated, 
these samples are generated with initial state QED radiation enabled. 
Comparisons with LEP and SLC data use $e^+e^-\rightarrow b\overline{b}$ samples
generated at $\sqrt{s}=91.2$ GeV. In addition, $e^+e^-\rightarrow b\overline{b}$ samples
generated at $\sqrt{s}=200$ GeV with initial state QED disabled for comparison to the $\sqrt{s}=91.2$ GeV samples. Comparisons with Belle and CLEO data are studied using  
$e^+e^-\rightarrow c\overline{c}$ samples with $\sqrt{s}=10.53$ GeV.

%The decay properties of bottom and charm hadrons for the four generators are studied  
%and are compared
For studies of bottom and charm hadron decay properties, \EvtGen~2.0~\cite{Lange:2001uf} is used.
Decay products of all heavy flavor hadrons are removed from the event record and the four-momenta
of the heavy flavor hadrons are passed to \EvtGen, which redecays these hadrons; these new decay
products are added to the event record.
In some cases, modifications to the \EvtGen\ default decay table have been made.  These changes
are discussed in Section~\ref{sec:decay}.
